|

### 2021-03-17 documentation/readme.Rmd
Added link to license in README
Delete "also".

`{britpol}` is an `R` package that makes analysing British political data quick and simple. It contains two pre-formatted datasets, plus a host of useful functions. The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia. The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. [Stata and SPSS versions of the data are also available too](https://github.com/jackobailey/britpol/tree/master/download).

@@

You may also use the `{britpol}` codebase for your own purposes in line with our license. But you must do so *with attribution*. That is, you may reproduce, reuse, and adapt the code as you see fit, but must state in each case that you used `{britpol}` to produce your work. The relevant citations are as follows:

>>>>

`{britpol}` is an `R` package that makes analysing British political data quick and simple. It contains two pre-formatted datasets, plus a host of useful functions. The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia. The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. [Stata and SPSS versions of the data are available too](https://github.com/jackobailey/britpol/tree/master/download).

@@

You may also use the `{britpol}` codebase for your own purposes in line with [our license](https://github.com/jackobailey/britpol/blob/master/LICENSE.md). But you must do so *with attribution*. That is, you may reproduce, reuse, and adapt the code as you see fit, but must state in each case that you used `{britpol}` to produce your work. The relevant citations are as follows:
